---
title: "DS 807 Lab 1"
author: "Nate Thomas"
date: "Due: 3/23/2021 by 11:59 pm"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align="center")

library(tidyverse)
library(tidytext)
library(wordcloud)
library(wordcloud2)
library(textdata)
library(igraph)
library(ggraph)
library(widyr)
```

## Lab Assignment Guidelines

#### Purpose:
  
- Learning Outcomes measured in this assignment: LO1, LO2, and LO3 

- Content knowledge you’ll gain from doing this assignment: Tokenization, word counts, visualization of frequent words, wordclouds, and sentiment analysis

#### Criteria:

- For this first lab, the grading criteria is 100% based on correctness of the code. 
- If you want feedback for your interpretations/communication of your findings, I will gladly do so, without penalizing for any possible errors in your comments/findings. Simply include them for all or selected questions.


#### Task

1. Install the required libraries if you have not done so.

2. For this lab, we will work with hotel review data for an eco-hotel (<https://www.areiasdoseixo.com/>). You can get full information form <https://archive.ics.uci.edu/ml/datasets/Eco-hotel#> The following chunk reads the data:

```{r}
hotel=read_csv("https://unh.box.com/shared/static/jhvj609uibhixieqoradol5x9bvvdb5r.csv")
```

3. Tokenize the data set by word and remove stop words.

```{r}
text_df=tibble(line=seq(1:nrow(hotel)), text=hotel$Review)
text_df

text_tidy=text_df %>%
  unnest_tokens(word, text)

text_tidy

text_tidy %>%
  count(word, sort=TRUE)
```
Removal of stop words
```{r}
text_tidy = text_tidy %>%
  anti_join(stop_words)

text_tidy %>%
  count(word, sort=TRUE)

```


4. Add "Areais", "do". "seixo", and "sexios" in the stop words and remove these as well.

```{r}
custom_stop_words <- tribble(
  # Column names should match stop_words
  ~word, ~lexicon,
  "Areais", "CUSTOM",
  "do", "CUSTOM",
  "seixo", "CUSTOM",
  "sexio", "CUSTOM"
)

stop_words2 <- stop_words %>% 
  bind_rows(custom_stop_words)

text_tidy = text_tidy %>%
  anti_join(stop_words2)

text_tidy %>%
  count(word, sort=TRUE)

```


5. Arrange the words in descending order by frequency and plot the 30 most frequent words.

```{r}
word_counts <- text_tidy %>% 
  count(word) %>% 
  top_n(30,n) %>%
  mutate(word2 = fct_reorder(word, n))

ggplot(word_counts, aes(x = word2, y = n)) +
  geom_col(show.legend=FALSE) +
  coord_flip() +
  ggtitle("Title")
```

5. Plot a word cloud of these 30 words (choose wordcloud or wordcloud 2).

```{r}
w_count = text_tidy %>%
  count(word)

wordcloud(word= w_count$word,
          freq=w_count$n,
          color="red",
          max.words=30)
```

6. Choose a sentiment library and perform a sentiment analysis, i.e., join the data with sentiments, count sentiments, plot sentiments.

```{r}
get_sentiments("loughran")

sentiment_text = text_tidy %>%
  inner_join(get_sentiments("loughran"))

sentiment_text %>%
  count(sentiment)

plotdata = sentiment_text %>%
  filter(sentiment %in% c("positive", "negative"))

sent_count =  plotdata %>%
  count(word, sentiment) %>%
  group_by(sentiment) %>%
  top_n(30, n) %>%
  ungroup() %>%
  mutate(word2=fct_reorder(word, n))

ggplot(sent_count, aes(x=word, y=n, fill=sentiment)) +
  geom_col(show.legend=FALSE)+
  facet_wrap(~sentiment, scales="free")+
  coord_flip()+
  labs(title = "Sentiment Word Counts", x="Words")

```

7. Is there any other analysis you wish to perform based on the things we learned today? If so, please go ahead and do include it/them here.

```{r}
data2=hotel
ngram_text = data2 %>%
  unnest_tokens(bigram, Review, token="ngrams", n=2)

ngram_text
```

```{r}
filtered_text = ngram_text %>%
  separate(bigram, c("word1", "word2"), sep=" ") %>%
  filter(!word1 %in% stop_words2$word) %>%
  filter(!word2 %in% stop_words2$word)

filtered_text
```

```{r}
bigram_count=filtered_text %>%
  count(word1, word2, sort=TRUE)

bigram_network = bigram_count %>%
  filter( n > 7) %>%
  graph_from_data_frame()

bigram_network

set.seed(1234)

ggraph(bigram_network, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```












